The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2024-02-20 index.qmd
revised presentation

text
- Transform two-mode network to one-mode university network showing number of schools visited by both university $i$ and university $j$

@@

### Slide w/ citation

#### Subtitle

Here's some text:

-   @RN4504 said blah...
-   Parenthetical citation [@RN4625].
-   **Bold** and *italic* text

More things:

-   Blah

>>>>

Construct two-mode network

- "Edge" or "network tie" = off-campus recruiting vist
- "Vertices” = schools $i$ (mode 1) and universities $j$ (mode 2)
text
- School-by-university matrix; cell $a_{i,j}$ shows number of visits school $i$ received from univ $j$

Transform two-mode network into one-mode university network

- university $i$ and university $j$ share an edge if they visit at least one high school in common
- "Weight" of the edge is number of high schools visited by both $i$ and $j$

### Visualizing two-mode recruiting network {.caption}

![](./assets/figures/plot_2mode_u.png)

@@

### Discussion

Key findings (for analysis sample)

- **RQ1**. Disproportionate number of visits to private schools
- **RQ2**. Substantial overlap in recruiting networks of public and private univs
- **RQ3**. For public univs, visit schools: in the South; Catholic/Christian; enrollment mostly white

Practical implications

- Universities should conduct an internal equity audit of recruiting practices

Implications for scholarship

- Selective private, public flagship compete for same affluent households
- @RN4935 study Ivy Plus admissions; focuses on student/household behavior
  - Ignore organizational linkages between privileged schools and univs
  - These orgs interact to increase flow of students between one another

### 2024-02-20 r_r/submission/manuscript_rihe_r_r.Rmd
revised presentation

A separate, multidisciplinary literature has analyzed linkages between private school and college access [@RN4935; @RN4407; @RN1565; @RN786]. This research observes strong links -- and student flows -- between private high schools and selective private universities. Private schools enroll many students who can afford private university tuition [@RN3519]. To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between private schools and colleges.

>>>>

A separate, multidisciplinary literature has analyzed linkages between private school and college access [@RN4935; @RN4407; @RN1565; @RN786; @RN3519]. This research observes strong links -- and student flows -- between private high schools and selective private universities. To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between private schools and colleges.
